---
title: "HW 04"
author: "INSERT YOUR NAME HERE"
format:
  html:
    embed-resources: true
toc: true
---

```{r load-packages, message = FALSE}

# - loading package manager
if (!require(pacman))
  install.packages(pacman)
# add any other packages you use here
pacman::p_load(tidyverse,
               openintro,
               patchwork,
               tigris,
               sf,
               readxl)

```
## 1 - A second chance
::: {.callout-note}
I chose to revise this set of plots from HM1 Question 3, because although the visualizations were informative and clearly illustrated the relationships, I lost 4 points for not organizing the multiple plots together using a layout tool. To improve this, I will combine these individual plots into a cohesive grid using the patchwork package, arranging them in a clear and logical format to facilitate direct comparison.
::: 

```{r}
#| label: label-me-1
#| warning: false
#| Massege: false
county_clean <- county |>
  filter(!is.na(homeownership),!is.na(poverty))

plot_a <- ggplot(county_clean, aes(x = homeownership, y = poverty))+
  geom_point()+
  labs(title = "Plot A")
  
plot_b <- ggplot(county_clean, aes(x = homeownership, y = poverty))+
  geom_point()+
  geom_smooth(method = "gam", se = FALSE, color = "Blue")+
  labs(title = "Plot B")

plot_c <- ggplot(county_clean, aes(x = homeownership, y = poverty, group = metro))+
  geom_point()+
  geom_smooth(method = "gam",se = FALSE, color = "Green")+
  labs(title = "Plot C")  

plot_d <- ggplot(county_clean, aes(x = homeownership, y = poverty, group = metro))+
  geom_smooth(method = "gam", se = FALSE, color = "Blue")+
  geom_point()+
  labs(title = "Plot D") 

plot_e <- ggplot(county_clean, aes(x = homeownership, y = poverty, group = metro))+
  geom_point(aes(color = metro))+
  geom_smooth(method = "gam", se = FALSE, color = "Blue", aes(linetype = metro))+
  guides(color = guide_legend(order = 2),    
    linetype = guide_legend(order = 1)) +
  labs(title = "Plot E") 

plot_f <- ggplot(county_clean, aes(x = homeownership, y = poverty, group = metro, color =   metro))+
  geom_point()+
  geom_smooth(method = "gam", se = FALSE, )+
  labs(title = "Plot F") 

plot_g <- ggplot(county_clean, aes(x = homeownership, y = poverty))+
  geom_point(aes(group = metro, color = metro))+
  geom_smooth(method = "gam",  se = FALSE, color = "Blue")+
  labs(title = "Plot G") 

plot_h <- ggplot(county_clean, aes(x = homeownership, y = poverty))+
  geom_point(aes(group = metro, color = metro))+
  labs(title = "Plot H")

# Grouping plots by using patchwork.
combined1_plot <- (plot_a | plot_b) /
                 (plot_c | plot_d)
combined1_plot + plot_annotation(title = "Comparison of Homeownership and Poverty Relationships Across U.S. Counties")

combined2_plot <-(plot_e | plot_f) /
                 (plot_g | plot_h)
combined2_plot



```


## 2.  Arizona state of counties

```{r}
#| label: label-me-2
options(tigris_use_cache = TRUE)
az_counties <- counties(state = "AZ", year = 2021, progress_bar = FALSE)
glimpse(az_counties)
```
```{r}
#| warning: false
#| Massege: false
ggplot(data = az_counties)+
  geom_sf(fill = "grey90") +
  geom_sf_text(aes(label = NAME), size = 3)+
  labs(x="Longitude",
       y="Latitude",
       title ="Conuties in Arizona State",
       caption = "Source: Shapefile obtained using {tigris} R package, v2.0.1")+
  theme_minimal()
```



## 3.  Arizona state of population change

```{r}
#| label: label-me-3
population_data<-read_excel("data/co-est2023-pop-04.xlsx", skip=4, n_max=16)
glimpse(population_data)
```
```{r}
population_data<-population_data|>
  rename(population_2020=`7186683`,
         population_2023=`7431344`)|>
## The following code to remove leading dots and trailing spaces was adapted from online solutions.
  mutate(Arizona=gsub("^\\.|\\s+$| County, Arizona", "", Arizona),
         total_pop_change_20_23 = population_2023-population_2020)
glimpse(population_data)         
```
```{r}
az_counties <- az_counties|>
  left_join(population_data, by = c("NAME"="Arizona"))
glimpse(az_counties)  
```
```{R}
#| warning: false
#| Massege: false
ggplot(data = az_counties)+
  geom_sf(aes(fill = total_pop_change_20_23)) +
  scale_fill_distiller(palette = "RdBu")+
  labs(x="Longitude",
       y="Latitude",
       title ="Counties in Arizona State",
       subtitle = "July 01,2020 to July 01,2023",
       caption = "Source: Shapefile obtained using {tigris} R package, v2.0.1 \npopulation data from US Census Bureau",
       fill = "Population change")+
  theme_minimal()
```

## 4.  Arizona state of Indiginous Tribal Regions

## 5. Arizona state of patchwork
